Exploring Determinants of Child Mortality Globally (2022): The Role of Vaccination, Healthcare Spending, and Nutrition

### 2025-04-14 paper/paper.qmd
Method

>>>>

# Method

To test the new metric and loss functions, we use the available strong lensing data for regression. We concatenate the features extracted from the CNN and contatenate them with the expert labels for regression. The result data has a total of ~ and ~ strong lenseing ones.

## New loss function

Here we will investigate two loss functions, ranknet loss and focal loss.
